---
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/muschellij2/actibase/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/muschellij2/actibase/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/muschellij2/actibase/branch/master/graph/badge.svg)](https://codecov.io/gh/muschellij2/actibase?branch=master)
[![Codecov test coverage](https://codecov.io/gh/muschellij2/actibase/graph/badge.svg)](https://app.codecov.io/gh/muschellij2/actibase)
<!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  cache = TRUE
)
```

# actibase Package

`actibase` is a baseline package for raw actigraphy and activity workflows.
It provides readers and core preprocessing helpers that downstream packages
can build on, such as step-count or summarization overlays.

## Installation

You can install `actibase` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("muschellij2/actibase")
```

## Quick start

```{r}
library(actibase)
gt3x_file = system.file(
  "extdata",
  "TAS1H30182785_2019-09-17.gt3x.gz",
  package = "actibase"
)
res = ab_read_gt3x(gt3x_file, verbose = FALSE)
res = ab_calibrate(res, verbose = FALSE)
res = ab_standardize_data(res)
resampled = ab_resample(res, sample_rate = 30L)
counts = ab_calculate_counts(resampled, 60L)
wear = ab_calculate_nonwear(counts)

head(counts)
head(wear)
```

## What lives here

`actibase` keeps the primitives that other packages can build on:

* file readers for GT3X and CWA input
* calibration and zero-filling helpers
* standardization and reshaping helpers
* resampling
* activity-count and non-wear calculation
* transformation bookkeeping

Higher-level summarization, step-count mapping, and downstream analysis
should live in overlay packages.
