---
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/jhuwit/actibase/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jhuwit/actibase/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jhuwit/actibase/branch/main/graph/badge.svg)](https://codecov.io/gh/jhuwit/actibase?branch=main)
<!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  cache = TRUE
)
```

# actibase Package

`actibase` is a baseline package for raw actigraphy and activity workflows.
It provides readers and core preprocessing helpers that downstream packages
can build on, such as step-count or summarization overlays.

## Installation

You can install `actibase` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("jhuwit/actibase")
```

## Quick start

```{r}
library(actibase)
res = acti_standardize_data(acti_raw_data)
resampled = acti_resample(res, sample_rate = 30L)
```

## What lives here

`actibase` keeps the primitives that other packages can build on:

* standardization and reshaping helpers
* resampling


Higher-level summarization, step-count mapping, and downstream analysis
should live in overlay packages.
